\texttt{davos}: a Python package ``smuggler'' for constructing lightweight reproducible notebooks

### 2022-10-19 paper/main.tex
remvoed advanced functionality section in favor of mention in impacts

\subsubsection{Additional functionality}
% - js functions
% - complex use cases

@@

Our work also has several more subtle ``advanced'' use cases and
potential impacts. Whereas Python's built-in \texttt{import}
statement is agnostic to packages' version numbers, \texttt{smuggle}
statements (when combined with onion comments) are version-sensitive.
This enables multiple versions of a single library to be
imported within the same notebook. This could be useful in cases
where specific features were added or removed from a package across
different versions, or in comparing the performance or functionality
of particular features across different versions of the same package.

>>>>

@@

Our work also has several more subtle ``advanced'' use cases and
potential impacts. Whereas Python's built-in \texttt{import}
statement is agnostic to packages' version numbers, \texttt{smuggle}
statements (when combined with onion comments) are version-sensitive.
And because onion comments are parsed at runtime, required package and
their specified versions are installed in a just-in-time manner. Thus, it is possible
in most cases to \texttt{smuggle} a specific package version or revision even if
a different version has already been loaded. This enables more complex uses
that take advantage of multiple versions of a package within a single interpreter
session. This could be useful in cases where specific features are added or
removed from a package across different versions, or in comparing the
performance or functionality of particular features across different versions of
the same package.
